Manuscript draft

### 2019-09-10 manuscript/manuscript draft.Rmd
manuscript updates

In order to approach these broad and complex issues, we simplify the major gaps in our knowledge to five key questions and corresponding specific predictions (Table 1):  
1.	How do carbon fluxes vary with latitude? 
2.	How do carbon fluxes relate to MAT and MAP?  
3.	How do carbon fluxes relate to other annual climate variables?  
4.	What is the role of seasonality in explaining variation in carbon fluxes?  
5.	Per month of the growing season, how does productivity vary with climate?

To resolve these questions, we require data that, firstly, control for variables influencing productivity, including stand age, disturbance regime, elevation, and methodology; and secondly includes all major carbon fluxes. Here we use a comprehensive global database of forest carbon fluxes to explore the above questions for nine carbon fluxes, allowing for an in-depth exploration of the effect of climate on global productivity.

>>>>

In order to approach these broad and complex issues, we simplify the major gaps in our knowledge to five key questions and corresponding specific predictions (Table 1). Firstly, we ask how forest autotrophic carbon fluxes (FACF) vary with latitude. We then test how these fluxes relate to MAT and MAP, and additionally how they respond to other, less well studied, climate variables. We finally consider the relationship between FACF and seasonality, considering the role of seasonality in explaining variation in carbon fluxes, and the influence of climate on FACF per month of the growing season.

Resolving these questions requires data which, firstly, control for variables influencing productivity, including stand age, disturbance regime, elevation, and methodology; and secondly includes all major carbon fluxes. Here we use a comprehensive global database of forest carbon fluxes to explore the above questions for nine carbon fluxes, allowing for an in-depth exploration of the effect of climate on global productivity.
